# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r, echo=TRUE}
# install.packages("data.table")
require(data.table)
setwd("C:/Users/Eric.Kim/Desktop/TSA Files/Coursera/Reproducible Research")
 
#Read file and subset
act<-read.csv("./activity.csv")
act$date<-as.Date(as.character(act$date, format="%Y%m%d"))
nacount<-sum(is.na(act$steps))
act<-subset(act, act$steps!= "NA")

#Aggregate by day
act<-data.table(act)
setkey(act, date)
steps<-data.frame(act[,sum(steps), by=date])
names(steps)[2]<-"stepnum"

```
## What is mean total number of steps taken per day?
```{r simpleplot}
#Histogram
hist(steps$stepnum, main = "Steps per Day Histogram", xlab="Steps per Day")
```

```{r}
#install required packages
require(MASS)
require(UsingR)
```

```{r}
#mean steps per day
m<-mean(steps$stepnum)
m
md<-median(steps$stepnum)
md
```


The mean is `r m`.  
The median is `r md`.  

## What is the average daily activity pattern?
```{r}
#Aggregate by interval
library(ggplot2)
require(ggplot2)
act<-data.table(act)
setkey(act, interval)
intrvl<-data.frame(act[,mean(steps), by=interval])
ggplot(data=intrvl, aes(x=interval, y=V1))+geom_line()
```

```{r}
max(intrvl$V1)
maxInterval<-subset(intrvl$interval, intrvl$V1==max(intrvl$V1))
```

The max interval is `r maxInterval`

There are `r nacount` NA's

## Imputing missing values
```{r}
setwd("C:/Users/Eric.Kim/Desktop/TSA Files/Coursera/Reproducible Research")

#Read file and subset
act2<-read.csv("./activity.csv")
act2$date<-as.Date(as.character(act2$date, format="%Y%m%d"))
act2[is.na(act2)]<- mean(na.omit(act2$steps))

#Aggregate by day
act2<-data.table(act2)
setkey(act2, date)
steps2<-data.frame(act2[,sum(steps), by=date])
```

```{r simpleplot2}
#Histogram
hist(steps2$V1, main = "Steps per Day Histogram with replacing NA", xlab="Steps per Day")
```

```{r}
#calculate mean and median
m2<-mean(steps2$V1)
m2
md2<-median(steps2$V1)
md2
```

After replacing NA with the mean steps, 
The new mean is `r m2`
The new median is `r md2`

## Are there differences in activity patterns between weekdays and weekends?
```{r}
act2$date2<-weekdays(act2$date)
act2$date3<-ifelse(act2$date2 %in% c("Monday", "Tuesday", "Wednesday", "Thursdsay", "Friday"), "Weekday", "Weekend")
```

```{r}
#Aggregate by interval by weekend/weekday
library(ggplot2)
require(ggplot2)
act2<-data.table(act2)
setkey(act2, interval, date3)
intrvl2<-data.frame(act2[,mean(steps), by=list(interval, date3)])
ggplot(data=intrvl2, aes(x=interval, y=V1))+geom_line()+facet_grid(.~date3)
```